---
title: "Using Social Media in Recruitment"
author: "Edmund Baker, Veronika Grimm, Yuval Ofek-Shanny"
output:
  xaringan::moon_reader:
    df_print: paged
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
      ratio: 16:9
    css: [my.pres2.css, default]
  slidy_presentation: default
  
---

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```
```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```

```{r global options, include=FALSE}
knitr::opts_chunk$set(#fig.path='Figs/', #fig.width=12, fig.height=8, 
                      echo=FALSE, warning=FALSE, message=FALSE,
                      out.extra = 'style="display:block; margin:auto;"')
library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(reshape)
library(tikzDevice)
library(plyr)
library(dplyr)
library(gtable)
library(grid)
library(gridExtra)
library(cowplot)
library(caroline)
library(ggpmisc)
library(tidyr)
library(plotly)
library(tidyquant)
library(lfe)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(arsenal)
library(knitr)
library(GGally)

cbp <- c("#999999", mh="#E69F00", g="#56B4E9", c="#009E73", nd="#F0E442", gl="#0072B2", b="#D55E00", "#CC79A7")
results = readRDS("C:\\Users\\fo06mafa\\Documents\\AuthenticApplications\\Data_amalgamate\\results.RDS")
player_table = readRDS("C:\\Users\\fo06mafa\\Documents\\AuthenticApplications\\Data_amalgamate\\player_table.RDS")

bin_function = function(column, number=3){ #column=results$mean_notelength
  breaks = quantile(column, na.rm = T, probs = seq(0,1, length.out=number+1)) 
  breaks = unique(breaks)
  #while(breaks[1] == breaks[2]){
  #  breaks = breaks[-1]
  #}
  tags <- vector(length=(length(breaks)-1))
  if((class(breaks) == "POSIXct")[1]){
    breakschar = strftime(breaks, format="%H:%M:%S")
    for(b in 2:length(breaks)){ #b=2
      tags[b-1] = paste0("[", breakschar[b-1], "-", breakschar[b], ")")
    }
  } else {
    for(b in 2:length(breaks)){ #b=2
      #tags[b-1] = paste0(gsub("0.",".", round(breaks[b-1], 2)), "-", gsub("0.",".", round(breaks[b],2)))
      tags[b-1] = paste0("[", round(breaks[b-1], 2), "-", round(breaks[b],2), ")")
      
    }
  }
  #if(strsplit(tags[1], split = "-")[2] %in% c("",".")){
  #  tags[1] = paste0("0", tags[1])
  #}
  group_tags <- cut(column, 
                    breaks=breaks, 
                    include.lowest=TRUE, 
                    right=FALSE, 
                    labels=tags)
  out <- factor(group_tags, 
                levels = tags,
                ordered = TRUE)
  return(out)
}

#var="notelength";  y.label = "Note Length"; y.positions = c(140, 145,150); tip.compar = 0.0005
bar.by.treat = function(var="notelength",  y.label = "Note Length", y.positions = c(140, 145,150), tip.compar = 0.0005){
  formula = as.formula(paste(var, "~", "treatment"))
  control.level = max(aggregate(formula, results, mean)[,2])*1.1
  stat.test <- compare_means(formula, data = results, method = "wilcox.test", ref.group = "control",
                             symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), 
                                                symbols = c("****", "***", "**", "*", "ns")))
  stat.test$y.position = c(control.level,
                           control.level,
                           control.level,
                           control.level,
                           control.level)  #y.positions
  stat.test$p.signif = gsub("ns", "", stat.test$p.signif)
  #stat.test$p.signif <- paste0(stat.test$p.signif, "*")
  #stat.test <- stat.test[c(1,4),]
  p1 = ggbarplot(results,
                 x = "treatment", 
                 y = var, 
                 fill= "treatment",
                 add = "mean_ci",
                 add.params = list(group ="treatment")
  )+
    theme_minimal() +
    stat_pvalue_manual(data = stat.test, 
                       label = "p.signif",
                       remove.bracket = T,
                     #  hide.ns = T,
                       tip.length = tip.compar
    ) +
    #lims(y=c(0,200)) +
    scale_fill_manual(values = c("control" = unname(cbp["c"]),
                                 "gap" = unname(cbp["g"]),
                                 "gap_lie" = unname(cbp["gl"]),
                                 "mental_health" = unname(cbp["mh"]),
                                 "no_data" = unname(cbp["nd"]),
                                 "bad" = unname(cbp["b"]))) +
    labs(fill="", y= y.label, x="") +
    theme(text = element_text(size=20),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          panel.grid.major.x = element_blank())
  p1 = p1 + coord_cartesian(ylim=c(0,(control.level*1.2)))
  return(p1)
}
#var="CV_score"; y.label = "CV score"; by="treatment"; y.positions=NA;  facet="experience_years"; refgroup="control"; x.label=""
#var="CV_score"; y.label = "CV score"; by="workExperienceInc"; y.positions=NA;  df=subset(results); facet="treatment"; refgroup = "0"; x.label=""
boxplot = function(var="CV_score", by="experience_years", df=results, facet=NA, refgroup=".all.", y.label = "CV score", x.label="", y.positions=NA, include.count=T){
  df[[by]] = factor(df[[by]], ordered=F)
  formula = as.formula(paste(var, "~", by))
  control.level = max(aggregate(formula, df, FUN = function(x){min(quantile(x, .75) + 0*IQR(x), max(x))})[,2])*1.1
  if(is.na(facet)){groupvar = NULL} else {groupvar = facet}
  stat.test <- compare_means(formula, data = df, method = "wilcox.test", ref.group = refgroup, group.by = groupvar,
                             symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), 
                                                symbols = c("****", "***", "**", "*", "ns")))
  
  if(is.na(y.positions)){stat.test$y.position = rep(control.level, nrow(stat.test))} else {stat.test$y.position = y.positions}
  stat.test$p.signif = gsub("ns", "", stat.test$p.signif)
  #stat.test$p.signif <- paste0(stat.test$p.signif, "*")
  #stat.test <- stat.test[c(1,4),]
  p1 = ggplot(df, aes_string(x=by, y=var, fill="treatment", group=by)) + 
    geom_boxplot(outlier.shape = NA, coef = 0) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="black", fill="black") +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0) +
    theme_minimal() 
  p1 = p1 + stat_pvalue_manual(data = stat.test, 
                               inherit.aes = FALSE,
                               label = "p.signif",
                               position = "identity",
                               remove.bracket = T,
                               #  hide.ns = T,
                               tip.length = tip.compar) # + lims(y=c(0,200)) 
  if(!is.na(facet)){p1 = p1 + facet_grid(as.formula(paste(".~", facet)), switch="both")}
  p1 = p1 + coord_cartesian(ylim=c(0,(control.level)))
  if("treatment" %in% c(by, facet)){
    p1 = p1 + scale_fill_manual(values = c("control" = unname(cbp["c"]),
                                                                           "gap" = unname(cbp["g"]),
                                                                           "gap_lie" = unname(cbp["gl"]),
                                                                           "mental_health" = unname(cbp["mh"]),
                                                                           "no_data" = unname(cbp["nd"]),
                                                                           "bad" = unname(cbp["b"]))) +
      theme(legend.position = "top",
            text = element_text(size=20),
            axis.ticks.x = element_blank(),
            panel.grid.major.x = element_blank()) + labs(fill="", y=y.label, x=x.label)
    if("treatment" %in% c(by)){p1 = p1 + theme(axis.text.x=element_blank())} else {p1 = p1 + theme(strip.text = element_blank())}
  } else {
    p1 = p1 + scale_fill_manual(values=c(rep(unname(cbp["a"]), length(unique(df[[by]]))))) +  
      theme(legend.position = "none",
            text = element_text(size=20),
            axis.ticks.x = element_blank(),
            panel.grid.major.x = element_blank()) + labs(fill="", y=y.label, x=x.label) 
  }
  if(include.count){
    p1 = p1 + theme(strip.text = element_blank(), axis.text.x=element_blank()) + labs(fill="", y=y.label, x="")
    p2 = ggplot(data = df, aes_string(x=by)) +
      geom_bar() +
      theme_minimal() +
      theme(legend.position = "none",
            axis.ticks.x = element_blank(),
            axis.text.y = element_blank(),
            panel.grid.minor.x = element_blank(),
            panel.grid.major.x = element_blank(),
            panel.grid.minor.y = element_blank())
    if(!is.na(facet)){p2 = p2 + facet_grid(as.formula(paste(".~", facet)), switch="both")}
    if("treatment" %in% c(by, facet)){
      p2 = p2 + theme(legend.position = "top",
                      text = element_text(size=20),
                      axis.ticks.x = element_blank(),
                      panel.grid.major.x = element_blank()) + labs(fill="", y="count", x=x.label)
      if("treatment" %in% c(by)){p2 = p2 + theme(axis.text.x=element_blank())} else {p2 = p2 + theme(strip.text = element_blank())}
    } else {
      p2 = p2 + scale_fill_manual(values=c(rep(unname(cbp["a"]), length(unique(df[[by]]))))) +  
        theme(legend.position = "none",
              text = element_text(size=20),
              axis.ticks.x = element_blank(),
              panel.grid.major.x = element_blank()) + labs(fill="", y="count", x=x.label) 
    }
    
    plot = cowplot::plot_grid(p1, p2, align = "v", nrow = 2, rel_heights = c(4/4, 1/4))
  } else {
    plot = p1
  }
   
  return(plot)
}
##### lines of best fit
#variable="CV_score";  by="SMcontents"; group="treatment"; df=results; include.count=T; x.label="Contents of the candidate's social media accounts (are important)"; leg.label = "Treatment"; cut.outliers=F
score.means.by.var.line2 <- function(variable, by, group, df, include.count=T, x.label="", leg.label="", cut.outliers=T){
  if(cut.outliers){df = df[!df[[by]] %in% boxplot.stats(df[[by]])$out,]}
  p1 = ggplot(df , aes_string(x=by, y=variable, group=group, colour=group)) + 
    geom_point(position=position_jitter(height=0), alpha=0.025) +
    #geom_ma(ma_fun = SMA, n = 20, linetype = 1, size = 1, na.rm = TRUE) +
    geom_smooth() +  # method=lm loess method=lm
    #lims(x=c(0,10)) +
    #geom_hline(yintercept = 0)+
    #facet_grid(treatment~.) +
    labs(y=variable, x=NULL) +
    theme_classic()
  p1 = p1 +  geom_hline(yintercept = mean(df[[variable]], na.rm=T)) + labs(colour = leg.label)
  if(group=="treatment"){
    p1 = p1 + scale_colour_manual(values = c("control" = unname(cbp["c"]),
                                             "gap" = unname(cbp["g"]),
                                             "gap_lie" = unname(cbp["gl"]),
                                             "mental_health" = unname(cbp["mh"]),
                                             "no_data" = unname(cbp["nd"]),
                                             "bad" = unname(cbp["b"])))
  }
  if(include.count){
    p1 = p1 + theme_minimal() +
      theme(#legend.title = element_blank(),
            legend.position = "top",
            panel.grid.major.x = element_blank(),
            panel.grid.minor.x = element_blank(),
            axis.text.x = element_blank(),
            axis.ticks.x = element_blank())
    p2 = ggplot(data = df, aes_string(x=by)) +
      geom_bar() +
      theme_minimal() +
      theme(legend.position = "none",
            axis.ticks.x = element_blank(),
            axis.text.y = element_blank(),
            panel.grid.minor.x = element_blank(),
            panel.grid.major.x = element_blank(),
            panel.grid.minor.y = element_blank())
    p2 = p2 + labs(x = x.label, colour=leg.label)
    plot = cowplot::plot_grid(p1, p2, align = "v", nrow = 2, rel_heights = c(4/4, 1/4))
  } else {
    p1 = p1 + theme_minimal() +
      theme(#legend.title = element_blank(),
            legend.position = "top",
            panel.grid.major.x = element_blank(),
            panel.grid.minor.x = element_blank())
    plot = p1
  }
  return(plot)
}

```

## Supporting internal validity
- People react as expected to the CVs, (more experience/education is better)

```{r, fig.width=12, fig.height=6}
p1 = boxplot(var="CV_score", y.label = "CV score", by="experience_years", y.positions=NA,  facet=NA, refgroup = "4", include.count = F)
p2 = boxplot(var="CV_score", y.label = "CV score", by="education_yt", y.positions=NA,  facet=NA, refgroup = "1", include.count = F)
cowplot::plot_grid(p1, p2, ncol = 2)

```
---

## Supporting internal validity
- People make effort and react to treatment 

```{r, fig.width=12, fig.height=6}
p1 = boxplot(var="notelength",  y.label = "Note Length Characters", by="treatment", y.positions=NA,  facet=NA, refgroup = "control", include.count = F)
p2 = boxplot(var="length_viewed",  y.label = "Minutes on CV", by="treatment", y.positions=NA,  facet=NA, refgroup = "control", include.count = F)
p3 = boxplot(var="no_times_viewed",  y.label = "Times Clicked on CV", by="treatment", y.positions=NA,  facet=NA, refgroup = "control", include.count = F)

legend = get_legend(p1 + theme(legend.position = "top"))
plots = cowplot::plot_grid(
  p1 + theme(legend.position = "none"),  
  p2 + theme(legend.position = "none"), 
  #  p3 + theme(legend.position = "none"),
  nrow = 1)

cowplot::plot_grid(legend, plots, ncol = 1, rel_heights = c(0.2, 2))

```
---

## SM information matters
```{r, fig.width=12, fig.height=7}
boxplot(var="CV_score",  y.label  = "CV score", by="treatment", y.positions=NA,  facet=NA, refgroup = "control", include.count = F)
```
---

## Experience and SM Treatment
```{r, fig.width=12, fig.height=7}
boxplot(var="CV_score",  y.label = "CV score", by="treatment", y.positions=NA,  facet="experience_years", refgroup = "control", include.count = F)
```
---

## Education and SM Treatment
```{r, fig.width=12, fig.height=7}
boxplot(var="CV_score",  y.label = "CV score", by="treatment", y.positions=NA,  facet="education_yt", refgroup = "control", include.count = F)
```
---

.reduced2[
```{r}
scaletab = function(LM_tab, scale_ind = T, scale = T, index){ #LM_tab = LM_tab[LM_tab$Treated1,]
  if(scale){
    if(scale_ind){
      LM_tab = subset(LM_tab, index)
    }
    for(v in formula_vars){
      if(is.numeric(LM_tab[[v]])){
        LM_tab[[v]] = scale(LM_tab[[v]])[,1]
      } else if(is.factor(LM_tab[[v]])){
        LM_tab[[v]] = factor(LM_tab[[v]], ordered = F)
      }
    }
    if(!scale_ind){
      LM_tab = subset(LM_tab, index)
    }
  }
  if(!scale){
    LM_tab = subset(LM_tab, index)
  }
  return(LM_tab)
}

############################ LINEAR MODELS ############################
y = "CV_score"
formula_vars = c(
  "experience_years",
  "education_yt" ,
  "skills_1.2", 
  "interests_1.2",
  "endorsements",
  "Female",
  "gap",
  "gap_lie",
  "mental_health",
  "no_data",
  "bad"
)
cluster_on = "mturkID" #"state" #
for_table<-gsub("_"," ", formula_vars)

formula =  paste(formula_vars, collapse = "+") %>%  paste("|0|0|", cluster_on) %>% paste(y,"~", ., sep="") %>% as.formula()

LM_tab = scaletab(results, index=rep(T,nrow(results)))
fitmodp = felm(keepX=TRUE, formula = formula, data = LM_tab)

LM_tab = results
fitmodp2 = felm(keepX=TRUE, formula = formula, data = LM_tab)

pl = c(#"(Intercept)" = "Intercept", 
  "experience_years" = "CV Experience", 
  "skills_1.2" = "CV Skills", 
  "interests_1.2" = "CV Interests", 
  "education_yt" = "CV Education", 
  "endorsements" = "SM Endorsements",
  "FemaleTRUE" = "Female", 
  "Order" = "Order",
  "skill_level" = "SM Skills",
  "gapTRUE" = "Gap",
  "gap_lieTRUE"= "Lie about Gap"     ,
  "mental_healthTRUE"= "Mental Health" ,
  "no_dataTRUE"= "No SM"      ,
  "badTRUE" = "Bad SM"
)

modellist = factor(c("Standardised", "Original"))
tab_model(fitmodp, fitmodp2,
          title="Linear Models",
          dv.labels = modellist, 
          pred.labels = pl, 
          show.ci = F, show.p = F, show.se=T, show.aic = T, show.intercept = F,
          string.pred = " ", string.est = gsub("_", " ", y),
          p.style = "stars", collapse.se = F
          )
```
]
---

```{r, fig.width=12, fig.height=7}
boxplot(var="CV_score", y.label = "CV score", by="treatment", y.positions=NA,  df=subset(results, gap|control), facet="workExperienceInc", refgroup = "control", x.label = "Noticed Work Experience Inconsistencies")
```
---

```{r, fig.width=12, fig.height=7}
boxplot(var="CV_score", y.label = "CV score", by="treatment", y.positions=NA,  df=subset(results, mental_health|control), facet="health", refgroup = "control", x.label = "Noticed 'Health Problems'")

```
---

```{r, fig.width=12, fig.height=7}
df. = results$age %>% bin_function(number = 5) %>% cbind(subgroup=. , results) %>% subset(mental_health|control) 
#boxplot(var="CV_score", y.label = "CV score", x.label = "age", by="treatment", y.positions=NA,  df=df., facet="subgroup", refgroup = "control")
boxplot(var="CV_score", y.label = "CV score", x.label = "age", by="subgroup", y.positions=NA,  df=df., facet="treatment", refgroup = levels(df.$subgroup)[1])




```
---

```{r, fig.width=12, fig.height=7}
boxplot(var="CV_score", y.label = "CV score", x.label = "lib_con", by="lib_con", y.positions=NA,  df=subset(results, mental_health|control), facet="treatment", refgroup = "1")

```
---


## Balance Table
.reduced2[
```{r}
############# tableby ################
form_pre = c("experience_years",
             "education_yt" ,
             "skills_1.2", 
             "interests_1.2",
             "Order")
formula = form_pre %>% paste(collapse = "+") %>% paste("treatment", "~", .) %>% as.formula() 
balance_table = tableby(formula, results, control = tableby.control(numeric.test = "kwt"))
tab1 = as.data.frame(summary(balance_table))

formula = "applicant.gender" %>% paste("treatment", "~", .) %>% as.formula() 
balance_table = tableby(formula, subset(results, !no_data), control = tableby.control(numeric.test = "kwt"))
tab2 = as.data.frame(summary(balance_table))
tab2 = cbind(tab2[,1:5], c("", "n/a", ""), tab2[6:8])
colnames(tab2) = colnames(tab1)
rbind(tab1, tab2) %>% kable()  
```
]
---

```{r fig.width=12, fig.height=8}
redcolssec = match(c("participant.gender", "age",  
                     "highest_education2", "marital_status2", "employment_status2",  
                     "lib_con", 
                     "SM_active",
                     # "lib_con", "Twitter", "Instagram", "Facebook", "Snapchat", "LinkedIn","TikTok",
                     "SM_approval",
                     # "stayintouch", "toomuchtime", "potentialemployers","professional", 
                     "privacy_no_problem",
                     #  "lostControl", "advertisers", "employers",  #privacy
                       "teams", "communicate", "administration", "customerService", "ITskills", 
                       "experience", "education", "hobbies", "CVcontents", "SMcontents", 
                     #"workExperienceIncLength", "educationIncLength","healthLength", "crimeLength", "discriminationLength", "anythingElseLength",
                     "total_time", "TimeSpentInstruc", "mean_no_times_viewed", "mean_notelength", 
                     "median_length_viewed", "min_length_viewed",
                     "control", "gap", "gap_lie", "mental_health", "no_data", "bad"
                  ),
                colnames(player_table))

tempdf = subset(player_table, select = redcolssec)
tempdf$participant.gender = revalue(tempdf$participant.gender,
                        c("Male"=0,
                          "Female" = 1,
                          "Other" = NA))

tempdf = apply(tempdf, 2, FUN = as.numeric)

#cor(tempdf, method = "pearson", use = "complete.obs")
ggcorr(tempdf)


```
---

## People who say education is important use education
```{r fig.width=12, fig.height=6}
score.means.by.var.line2("CV_score", "education","education_yt.factor",  results, include.count=T, cut.outliers = F, x.label="Candidate's Education (is important)", leg.label = "Years Education")

```
---

## People who say experience is important use experience
```{r fig.width=12, fig.height=6}
score.means.by.var.line2("CV_score", "experience","CV.experience.factor",  results, include.count=T, cut.outliers = F, x.label="Candidate's Experience (is important)", leg.label = "Years Experience")
```
---

## People who say CV is important use experience
```{r fig.width=12, fig.height=6}
score.means.by.var.line2("CV_score", "CVcontents","CV.experience.factor",  results, include.count=T, cut.outliers = F, x.label="Contents of the candidate's CV (is) important)", leg.label = "Years Experience")

```
---

## People who say SM is important use SM
```{r fig.width=12, fig.height=6}
score.means.by.var.line2("CV_score", "SMcontents","treatment",  results, include.count=T, cut.outliers = F, x.label="Contents of the candidate's social media accounts (are important)", leg.label = "Treatment")
```
---
## Conclusions

.bullet-content[

]

---


