---
title: "Using Social Media in Recruitment"
author: "Edmund Baker, Veronika Grimm, Yuval Ofek-Shanny"
output:
  xaringan::moon_reader:
    df_print: paged
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
      ratio: 16:9
    css: [my.pres2.css, default]
  slidy_presentation: default
  
---

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```
```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```

```{r global options, include=FALSE}
knitr::opts_chunk$set(#fig.path='Figs/', #fig.width=12, fig.height=8, 
                      echo=FALSE, warning=FALSE, message=FALSE,
                      out.extra = 'style="display:block; margin:auto;"')

setwd("C:\\Users\\fo06mafa\\Documents\\AuthenticApplications")

library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(reshape)
library(tikzDevice)
library(plyr)
library(dplyr)
library(gtable)
library(grid)
library(gridExtra)
library(cowplot)
library(caroline)
library(ggpmisc)
library(tidyr)
library(plotly)
library(tidyquant)
library(lfe)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(arsenal)
library(knitr)
library(GGally)

reverse_legend_labels <- function(plotly_plot) {
  n_labels <- length(plotly_plot$x$data)
  plotly_plot$x$data[1:n_labels] <- plotly_plot$x$data[n_labels:1]
  plotly_plot
}
```

## Supporting internal validity
- People exert effort reviewing applications

.pull-left[
```{r, fig.asp=1, fig.width=6}
length_viewed_hist = readRDS(file = "..\\exhibits\\length_viewed_hist.RDS")
length_viewed_hist

```
]
.pull-right[
```{r, fig.asp=1, fig.width=6}
notelegnth_hist = readRDS(file = "..\\exhibits\\notelegnth_hist.RDS")
notelegnth_hist
```
]
---

## Supporting internal validity
- People react to treatment

.pull-left[
```{r, fig.asp=1, fig.width=6}
lengthViewed_tr_boxplot = readRDS(file = "..\\exhibits\\lengthViewed_tr_boxplot.RDS")
lengthViewed_tr_boxplot
```
]
.pull-right[
```{r, fig.asp=1, fig.width=6}
notelength_tr_boxplot = readRDS(file = "..\\exhibits\\notelength_tr_boxplot.RDS")
notelength_tr_boxplot
```
]
---

## Supporting internal validity
- People react as expected to the CVs, (more experience/education is better)

.pull-left[
```{r, fig.asp=1, fig.width=6}
exp_boxplot = readRDS(file = "..\\exhibits\\exp_boxplot.RDS")
exp_boxplot

```
]
.pull-right[
```{r, fig.asp=1, fig.width=6}
educ_boxplot = readRDS(file = "..\\exhibits\\educ_boxplot.RDS")
educ_boxplot
```
]
---

## SM information matters
```{r, fig.asp=0.6 fig.width=12}
tr_boxplot = readRDS(file = "..\\exhibits\\tr_boxplot.RDS")
tr_boxplot
```
---

.reduced2[
```{r}
linearModel_tr_tab1 = readRDS(file = "..\\exhibits\\linearModel_tr_tab1.RDS")
linearModel_tr_tab1
```
]
.pull-right2[
```{r,  fig.asp=1.01, fig.width=8}
linearModel_tr_plot1 = readRDS(file = "..\\exhibits\\linearModel_tr_plot1.RDS")
ggplotly(linearModel_tr_plot1) %>% layout(legend = list(orientation = "h")) %>% reverse_legend_labels()
```
]
---

.reduced[
```{r}
linearModel_tr_tab2 = readRDS(file = "..\\exhibits\\linearModel_tr_tab2.RDS")
linearModel_tr_tab2
```
]
.pull-right2[
```{r,  fig.asp=1.01, fig.width=8}
linearModel_tr_plot2 = readRDS(file = "..\\exhibits\\linearModel_tr_plot2.RDS")
ggplotly(linearModel_tr_plot2) %>% layout(legend = list(orientation = "h")) %>% reverse_legend_labels()
```
]
---

## Experience and SM Treatment
```{r, fig.asp=0.6 fig.width=12}
exp_tr_boxplot3 = readRDS(file = "..\\exhibits\\exp_tr_boxplot3.RDS")
exp_tr_boxplot3
```
---

.reduced3[
```{r}
linearModel_tr_tab3 = readRDS(file = "..\\exhibits\\linearModel_tr_tab3.RDS")
linearModel_tr_tab3
```
]
.pull-right3[
```{r,  fig.asp=0.85, fig.width=10.5}
linearModel_tr_plot3 = readRDS(file = "..\\exhibits\\linearModel_tr_plot3.RDS")
ggplotly(linearModel_tr_plot3) %>%layout(legend = list(orientation = "h")) %>% reverse_legend_labels()
```
]
---

## People who noticed gaps.
```{r, fig.asp=0.6 fig.width=12}
noticWorkExpInc_boxplot = readRDS(file = "..\\exhibits\\noticWorkExpInc_boxplot.RDS")
noticWorkExpInc_boxplot
```
---

## People who noticed health problems.
```{r, fig.asp=0.6 fig.width=12}
noticHealth_boxplot = readRDS(file = "..\\exhibits\\noticHealth_boxplot.RDS")
noticHealth_boxplot
```
---

## Age
```{r, fig.asp=0.6 fig.width=12}
ageMentalHelath_boxplot = readRDS(file = "..\\exhibits\\ageMentalHelath_boxplot.RDS")
ageMentalHelath_boxplot
```
---

## Conservatives
```{r, fig.asp=0.6 fig.width=12}
libConMentalHealth_boxplot = readRDS(file = "..\\exhibits\\libConMentalHealth_boxplot.RDS")
libConMentalHealth_boxplot
```
---

## Active on SM
```{r, fig.asp=0.6 fig.width=12}
SMActiveno_data_boxplot = readRDS(file = "..\\exhibits\\SMActiveno_data_boxplot.RDS")
SMActiveno_data_boxplot
```
---

## People who believe SM is a tool
```{r, fig.asp=0.6 fig.width=12}
potentialEmployersBad_boxplot = readRDS(file = "..\\exhibits\\potentialEmployersBad_boxplot.RDS")
potentialEmployersBad_boxplot
```
---

## People who believe SM is Important
```{r, fig.asp=0.6 fig.width=12}
SMContentBad_boxplot = readRDS(file = "..\\exhibits\\SMContentBad_boxplot.RDS")
SMContentBad_boxplot
```
---

## People who say SM is important use SM
```{r, fig.asp=0.6 fig.width=12}
trSMImp_lineplot = readRDS(file = "..\\exhibits\\trSMImp_lineplot.RDS")
trSMImp_lineplot
```
---

## People who say education is important use education
```{r, fig.asp=0.6 fig.width=12}
educEducImp_lineplot = readRDS(file = "..\\exhibits\\educEducImp_lineplot.RDS")
educEducImp_lineplot
```
---

## People who say experience is important use experience
```{r, fig.asp=0.6 fig.width=12}
expEXpImp_lineplot = readRDS(file = "..\\exhibits\\expEXpImp_lineplot.RDS")
expEXpImp_lineplot
```
---



.reduced3[
```{r}
BLP_tr_tab = readRDS(file = "..\\exhibits\\BLP_tr_tab.RDS")
BLP_tr_tab
```
]
.pull-right3[
```{r,  fig.asp=0.85, fig.width=10.5}
BLP_tr_plot = readRDS(file = "..\\exhibits\\BLP_tr_plot.RDS")
ggplotly(BLP_tr_plot) %>%layout(legend = list(orientation = "h")) %>% reverse_legend_labels()
```
]
---

.pull-left[
```{r, fig.asp=1.3, fig.width=7}
linearModel_tr_plot3 = readRDS(file = "..\\exhibits\\linearModel_tr_plot3.RDS")
ggplotly(linearModel_tr_plot3) %>%layout(legend = list(orientation = "h")) %>% reverse_legend_labels()
```
]
.pull-right[
```{r,  fig.asp=1.3, fig.width=7}
BLP_tr_plot = readRDS(file = "..\\exhibits\\BLP_tr_plot.RDS")
ggplotly(BLP_tr_plot) %>%layout(legend = list(orientation = "h")) %>% reverse_legend_labels()
```
]
---

##CATE
```{r, fig.asp=0.6 fig.width=12}
CATE_hist = readRDS(file = "..\\exhibits\\CATE_hist.RDS")
CATE_hist
```
---

```{r fig.asp=0.66, fig.width=12}
corr_plot = readRDS(file = "..\\exhibits\\corr_plot.RDS")
corr_plot
```
---



.reduced[
```{r}
tableby1 = readRDS(file = "..\\exhibits\\tableby1.RDS")
#tableby1 %>% kable()
```
]

## Conclusions

.bullet-content[

]

---

## Education and SM Treatment
```{r, fig.asp=0.5, fig.width=12}
educ_tr_boxplot = readRDS(file = "..\\exhibits\\educ_tr_boxplot.RDS")
educ_tr_boxplot
```
---

