---
title: "Is the Endowment Effect a rational response to the Winner's Curse?"
author: "Ed Baker"
output:
  xaringan::moon_reader:
    df_print: paged
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
      ratio: 16:9
    css: [my.pres.css, default]
  slidy_presentation: default
---

```{r xaringan-panelset, echo=FALSE, warning=FALSE}
xaringanExtra::use_panelset()
```

```{r xaringan-tile-view, echo=FALSE, warning=FALSE}
xaringanExtra::use_tile_view()
```

```{r setup, include=FALSE, warning=FALSE}
options(htmltools.dir.version = FALSE)
```

## Puzzle

.bullet-content[
- In Behavioural Economics there is a WTP-WTA gap attributed to bias.
- In Financial Market Modeling there is the bid-ask spread attributed to a rational response to asymmetric information.
]

--

```{r echo = FALSE, fig.width=4,fig.height=4, fig.align='center'}
library(ggplot2)
print(ggplot() +
  lims(x=c(0, 1),
       y= c(0, 1)) +
  theme_classic() + 
  labs(title="Types of Goods", y="Value Uncertainty", x="Correlation of Value"))
```

---

## Information not Important
.bullet-content[
\begin{align*}
 WTP(x) &= \mathbb{E}(x) \\
 WTA(x) &= \mathbb{E}(x) \\
 WTP(x) &= WTA(x)
\end{align*}
]

--

## Information Important
.bullet-content[
\begin{align*}
 WTP(x) &= \mathbb{E}(x|\textrm{ someone wants to sell }x) \\
 WTA(x) &= \mathbb{E}(x|\textrm{ someone wants to buy }x) \\
 WTP(x) &\leq WTA(x)
\end{align*}
]

---

## Claim

.bullet-content[
if..
1. Agents do not know the value of $x$.
2. Agents values of $x$ are correlated

then  
$$ WTP(x) < WTA(x) $$
]

---

## Agents do not know the value of x.

.bullet-content[
- The easy case:
    - Goods with Resale value
    - New Unknown Goods (books, films)
- But also consider the mug:
    - I am not a mug expert
    - I want to own mugs other people find attractive
    - I cannot perfectly predict how I will feel about the mug in the future
    - I do not know what else is available
    - To know the dollar value of a mug is to know the EU of the mug and the EU of a dollar
    - If there is any information that could cause me to change my valuation, then there is uncertainty

]

---

## Similar to ...

.bullet-content[
- Winners Curse  
- No trade Theorem: Aumann (1976) 
- Market for Lemons, Asymmetric Information: Akerlof (1978) 
- Herding: Banerjee (1992)
- Social Learning Models 
- Frenkel et al. (2018)
- Dupont and Lee (2002)
- Bruner, Calegari and Handfield (2020)
]

---

## Model
.pull-left[

**GAME**

Players:  
$i \in \{B, S\}$, one Buyer and one Seller.  
Strategies:  
$s_S = WTA \in \mathbb{R}$  
$s_B = WTP \in \mathbb{R}$  
Payoffs:  
$u_S = p - v_S$ if transaction else $0$  
$u_B = v_B - p$ if transaction else $0$  

**ORDER**

1. Nature chooses $v_i$ and $s_i$ 
2. $i$ observes $s_i$   
3. Buyer chooses WTP, Seller chooses WTA  
4. Nature chooses $p$ randomly (BDM), transaction if $WTA < p < WTP$
]

.pull-right[
**VARIABLES**

$v_i$ : &nbsp; Value of object to Person $i$.  
$\qquad$ $\mathbb{E}(V) = \mu$  
$\qquad$ $\mathbb{V}(V) = \sigma_d^2$  
$s_i$ : &nbsp; Noisy unbiased signal of $v_i$ observed by $i$.  
$\qquad$ $\mathbb{E}(S_i) = v_i$  
$\qquad$ $\mathbb{V}(S_i) = \sigma_i^2$  
$p$ : &nbsp; transaction price  
$\qquad$ $p \in \mathbb{R}$
]
---

## Model (Normal)
.pull-left[

**GAME**

Players:  
$i \in \{B, S\}$, one Buyer and one Seller.  
Strategies:  
$s_S = WTA \in \mathbb{R}$  
$s_B = WTP \in \mathbb{R}$  
Payoffs:  
$u_S = p - v_S$ if transaction else $0$  
$u_B = v_B - p$ if transaction else $0$  

**ORDER**

1. Nature chooses $v_i$ and $s_i$ 
2. $i$ observes $s_i$   
3. Buyer chooses WTP, Seller chooses WTA  
4. Nature chooses $p$ randomly (BDM), transaction if $WTA < p < WTP$
]

.pull-right[
**VARIABLES**

$v_i$ : &nbsp; Value of object to Person $i$.  
$\qquad$ $\sim N(\mu, \sigma_d^2)$  
$s_i$ : &nbsp; Noisy unbiased signal of $v_i$ observed by $i$.  
$\qquad$ $\sim N(v_i, \sigma_i^2)$  
$p$ : &nbsp; transaction price  
$\qquad$ $p \in \mathbb{R}$  
]
---


## Predictions

.bullet-content[

- $GAP_i(\sigma_i, \sigma_d)$ is increasing in $\sigma_i$ and decreasing in $\sigma_d$
- The greater the uncertainty of value, the greater the gap
- The greater the similarity, the greater the gap 
]

---

## Info Based Approach Explains

.bullet-content[
- Experienced traders do not have Endowment Effect (List, 2003)
- Smaller Endowment Effect when items are similar (Chapman, 1998)
- Bigger WTP-WTA gaps for non-market goods (Tunçel & Hammitt, 2014)
- Endowment Effect sometimes vanishes (Plott & Zeiler, 2007)

]

--

### and more vaguely and generally (?)

.bullet-content[
Herding, Fads and Fashions, Booms and Busts, Imitation, Conformity, Social Proof, Preferences correlated across cultures, Advertising Techniques, Status Quo Bias, preference reversal.
]

---

## Experiment 1: The Model Itself

.bullet-content[
- Explain RV drawn from distribution (or with balls from urns).  
- Elicit WTP/WTA  
- Vary (dis)similarity
- Vary uncertainty
- Could be unnatural?
]
 
---

## Experiment 2: Vernon Smith Style

.bullet-content[
- Elicit WTA/WTP for lotteries for tokens.  
- Vary the (dis)similarity via
  - tokens worth different amounts for different participants.
]

---

## Experiment 3: Lotteries for Money

.bullet-content[
- Elicit WTA/WTP for lotteries.  
- Vary 'uncertainty' via 
  1. Complexity of lotteries
  2. Number of practice draws
  3. Decision time  
  4. Maths test score
- Vary (dis)similarity via 
  1. Risk aversion score visible to both $i$ and $j$

  
]

---

## Experiment 4: Goods

.bullet-content[
- Elicit WTP/WTA for goods
- Vary 'uncertainty' via:
  1. Decision time 
  2. Giving more information about the goods
  3. Ask questions that force participants to think about value
- Vary (dis)similarity via
  1. with Genderised vs non-genderised goods + reveal gender?
  2. goods with high variation i.e. some people use them a lot, other people rarely.
  e.g. shoes + Shoe size?
  
]

---

## Experiment 5: Teams

.bullet-content[
- Elicit WTP/WTA for goods or lotteries
- Decisions made  alone vs in teams of two (with chat)
- They must agree, but then each receive or pay full p
- Could increase effort or model as two independent signals
- Teams should have smaller gaps than individuals.
]

---

## Experiment 6: Exchange with whom?

.bullet-content[
- Elicit WTP/WTA for goods.
- Vary dis(similarity):  
  - exchange with experimenter vs  
  - exchange with fellow student vs
  - exchange with fellow student who already owns a lot of said good
- repeat with different goods, swapping buying and selling roles, one being chosen at the end
]

---

## Experiment 7: Similar Goods

.bullet-content[
- Ask willing to Exchange
- Vary 'uncertainty' via:
 - changing the goods: (similar goods, smaller gap)
- Already done (Chapman, 1998)
]

---

## Experiment 8: Extra Info

.bullet-content[
- Ask willing to Exchange 
- Give info: either  
  1. Another person was not willing to exchange, vs
  2. Another person was willing to exchange
- Could be unnatural?  
]

---

## Experiment 9: Find an Object

.bullet-content[
- Ask willing to Exchange 
- Frame with a story: either  
  1. You meet another individual, would you trade with them?
  2. You find object, but you only have space for one in your bag
- Could seem artificial?  
]

---

# Thanks for listening


